Sparsely Activated Networks

### 2020-11-11 ms.tex
extract reproducibility code from ms.tex to Makefile
init

\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}

@@

\begin{figure*}[!t]
	\centering
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-identity-1d-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-relu-1d-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-topk-absolutes-1d-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-extrema-pool-indices-1d-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-extrema-1d-2-activations-0}}
	\\
	\setcounter{subfigure}{0}
	\subfloat[Identity]{\includegraphics[width=0.2\textwidth]{results/MNIST-identity-2d-2-activations-1}\label{subfig:identity}}
	\subfloat[ReLU]{\includegraphics[width=0.2\textwidth]{results/MNIST-relu-2d-2-activations-0}\label{subfig:relu}}
	\subfloat[top-k absolutes]{\includegraphics[width=0.2\textwidth]{results/MNIST-topk-absolutes-2d-2-activations-0}\label{subfig:topkabsolutes}}
	\subfloat[Extrema-Pool indices]{\includegraphics[width=0.2\textwidth]{results/MNIST-extrema-pool-indices-2d-2-activations-0}\label{subfig:extremapoolindices}}
	\subfloat[Extrema]{\includegraphics[width=0.2\textwidth]{results/MNIST-extrema-2d-2-activations-0}\label{subfig:extrema}}
	\caption{Visualization of the activation maps of five activation functions (Identity, ReLU, top-k absolutes, Extrema-Pool indices and Extrema) for 1D and 2D input in the top and bottom row respectively.
	The 1D input to the activation functions is denoted with the continuous transparent green line using an example from the UCI dataset.
	The output of each activation function is denoted with the cyan stem lines with blue markers.
	The 2D example depicts only the output of the activation functions using an example from the MNIST dataset.
	}
	\label{fig:activationfunctions}
\end{figure*}

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-signal}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-reconstructed}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-reconstruction-0}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-activations-0}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-similarity-0}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{results/UCI-epilepsy-extrema-1d-2-kernel-0}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-signal}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-reconstructed}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-reconstruction-0}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-activations-0}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-similarity-0}};
			\node[opacity=0, left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{results/UCI-epilepsy-extrema-1d-2-kernel-0}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-reconstruction-1}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-activations-1}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-1d-2-similarity-1}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{results/UCI-epilepsy-extrema-1d-2-kernel-1}};

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-signal}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-reconstructed}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-reconstruction-0}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-activations-0}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-similarity-0}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{results/MNIST-extrema-2d-2-kernel-0}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-signal}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-reconstructed}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-reconstruction-0}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-activations-0}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-similarity-0}};
			\node[opacity=0, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{results/MNIST-extrema-2d-2-kernel-0}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-reconstruction-1}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-activations-1}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/MNIST-extrema-2d-2-similarity-1}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{results/MNIST-extrema-2d-2-kernel-1}};

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-relu-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-relu-1d-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-topk-absolutes-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-topk-absolutes-1d-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-extrema-pool-indices-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-extrema-pool-indices-1d-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-extrema-1d-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-extrema-1d-1-kernel-0}

>>>>

@@

\begin{figure*}[!t]
	\centering
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-identity-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-relu-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-top-k-absolutes-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-extrema-pool-idx-2-activations-0}}
	\subfloat{\includegraphics[width=0.2\textwidth]{results/UCI-epilepsy-extrema-2-activations-0}}
	\\
	\setcounter{subfigure}{0}
	\subfloat[Identity]{\includegraphics[width=0.2\textwidth]{results/MNIST-identity-2-activations-1}\label{subfig:identity}}
	\subfloat[ReLU]{\includegraphics[width=0.2\textwidth]{results/MNIST-relu-2-activations-0}\label{subfig:relu}}
	\subfloat[top-k absolutes]{\includegraphics[width=0.2\textwidth]{results/MNIST-top-k-absolutes-2-activations-0}\label{subfig:topkabsolutes}}
	\subfloat[Extrema-Pool indices]{\includegraphics[width=0.2\textwidth]{results/MNIST-extrema-pool-idx-2-activations-0}\label{subfig:extremapoolindices}}
	\subfloat[Extrema]{\includegraphics[width=0.2\textwidth]{results/MNIST-extrema-2-activations-0}\label{subfig:extrema}}
	\caption{Visualization of the activation maps of five activation functions (Identity, ReLU, top-k absolutes, Extrema-Pool indices and Extrema) for 1D and 2D input in the top and bottom row respectively.
	The 1D input to the activation functions is denoted with the continuous transparent green line using an example from the UCI dataset.
	The output of each activation function is denoted with the cyan stem lines with blue markers.
	The 2D example depicts only the output of the activation functions using an example from the MNIST dataset.
	}
	\label{fig:activationfunctions}
\end{figure*}

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-signal}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-reconstructed}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-reconstruction-0}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-activations-0}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-similarity-0}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{results/UCI-epilepsy-extrema-2-kernel-0}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-signal}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-reconstructed}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-reconstruction-0}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-activations-0}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-similarity-0}};
			\node[opacity=0, left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{results/UCI-epilepsy-extrema-2-kernel-0}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-reconstruction-1}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-activations-1}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/UCI-epilepsy-extrema-2-similarity-1}};

@@

			\node[left=1.5cm of conv2] (kernel){\includegraphics[scale=0.1]{results/UCI-epilepsy-extrema-2-kernel-1}};

@@

			\node[opacity=0] at (0, 0)(input){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-signal}};

@@

			\node[opacity=0, right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-reconstructed}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-reconstruction-0}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-activations-0}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-similarity-0}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{results/MNIST-extrema-2-kernel-0}};

@@

			\node[] at (0, 0)(input){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-signal}};

@@

			\node[right=0.5cm of loss] (reconstructed){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-reconstructed}};

@@

			\node[opacity=0, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-reconstruction-0}};

@@

			\node[opacity=0, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-activations-0}};

@@

			\node[opacity=0, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-similarity-0}};
			\node[opacity=0, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{results/MNIST-extrema-2-kernel-0}};

@@

			\node[opacity=0.8, below=0.5cm of plus] (reconstruction){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-reconstruction-1}};

@@

			\node[opacity=0.8, below=0.5cm of conv2] (extrema){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-activations-1}};

@@

			\node[opacity=0.8, left=0.55cm of phi] (similarity){\includegraphics[scale=\figscale]{results/MNIST-extrema-2-similarity-1}};
			\node[opacity=0.8, left=1.2cm of conv2] (kernel){\includegraphics[scale=0.1]{results/MNIST-extrema-2-kernel-1}};

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-relu-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-relu-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-top-k-absolutes-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-top-k-absolutes-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-extrema-pool-idx-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-extrema-pool-idx-1-kernel-0}

@@

	\includegraphics[width=0.06\textwidth]{results/apnea-ecg-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bidmc-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/bpssrat-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/cebsdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/ctu-uhb-ctgdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/drivedb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/emgdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/mitdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/noneeg-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/prcp-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/shhpsgdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/slpdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/sufhsdb-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/voiced-extrema-1-kernel-0}
	\includegraphics[width=0.06\textwidth]{results/wrist-extrema-1-kernel-0}
